---
title:
#output:
#  rmdformats::material:
#    highlight: kate
---


```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=F, cache=T, prompt=F, tidy=T, comment=NA, message=F, warning=F)
opts_knit$set(width=75)
```

# Petición
`r peticion$Título` 

# Descripción 
`r peticion$Descripción` 

# Caso de ilegitimidad
`r peticion$Caso`

# Fecha de envío
`r peticion[["Fecha envío"]]`

# Medio
`r peticion$Medio`

# Copia de la petición
`r peticion[["Copia peticion"]][[1]]$url`

# Respuesta
`r if (is.na(peticion$Comentarios)) "" else peticion$Comentarios`

# Tiempo respuesta
`r if (is.na(peticion[["Tiempo respuesta"]])) "" else paste(peticion[["Tiempo respuesta"]],"días")`

# Valoración respuesta
`r if (is.na(peticion[["Valoración respuesta"]])) "" else peticion[["Valoración respuesta"]]`

# Copia de la respuesta
```{r, results="asis"}
docs <- peticion[["Copia respuesta"]][[1]]
if (length(docs)>0){
  for (i in 1:nrow(docs)){
    cat("- [", docs[i,"filename"], "](", docs[i,"url"], ")\n")
  }
}
```

